IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/extensions.tex
nits

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy |alpha|, which
maps a task list to a potentially different task list, i.e.,
$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
We described two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies based on the
current task list---in fact, our formalism can be easily 
extended to consider history~\cite{BartheRRS07}.
%
As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
which always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
More precisely, our calculus generalizes to a class of deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
%greatest lower bound of all the labels on the task labels,\footnote{
%  The label on a task's current label is the current label of the
%  parent at the time of creation, i.e., the initial current label of
%  the task.
%} 
scheduling decisions on public tasks do not depend on a sensitive task's
state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
is a task in the task list whose label is below (or incomparable to) the label
of another task, this task (or another one at the same level) must eventually
run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

>>>>

\subsection{Scheduling Policies}
Our specification language is parametrized by a scheduling policy |alpha|, which
maps a task list to a potentially different task list, i.e.,
$\alpha_{{\tiny\mathrm{\text{step}}}}(\ifc{\Varid{t}},\ldots)$. 
%
As previously discussed, the precise definition of |alpha|
dictates whether the language is TSNI, TINI, or neither.
%
We described two popular policies |roundrobinf| and
|seqf| for which we showed TSNI and TINI, respectively.
%
However, our definitions allow for other scheduling policies based on the
current task list---in fact, our formalism can be easily 
extended to consider history~\cite{BartheRRS07}.
%
As an example of generality, our approach allows to implement the scheduler of~\cite{Kashyap:2011}
which always schedules less sensitive threads first; this can be
employed to address external timing covert channels where an attacker
can measure the delay between output events.\footnote{
  When considering a label lattice that is not totally ordered, e.g.,
  DLM~\cite{myers:dlm} or DCLabels~\cite{dclabels}, this scheduling policy is
  considerably more complex.
}
%
More precisely, our calculus generalizes to a class of deterministic
schedulers that are: 1) \emph{integrity-preserving}, i.e., they do not
modify (or create) tasks; 2) \emph{non-interferent}, i.e., 
%greatest lower bound of all the labels on the task labels,\footnote{
%  The label on a task's current label is the current label of the
%  parent at the time of creation, i.e., the initial current label of
%  the task.
%} 
scheduling decisions on public tasks do not depend on a sensitive task's
state~\cite{russo2006securing}; and, 3) make \emph{low-progress}, i.e., if there
is a task in the task list whose label is below (or incomparable to) the label
of another task, this task (or another one at the same level) must eventually
run.
%
The last condition is required for TSNI; languages relying on
schedulers, such as |seqf|, that do not satisfy the low-progress
condition can at most satisfy TINI.
%
For simplicity, we do not treat this, more-general class of schedulers;
doing so would require modifying our calculus to keep track of the
label on the current label of tasks and complicate the
non-interference proofs.

### 2014-07-08 paper/real.tex
nits

JavaScript as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O
(we denote this language as |targetLangJS|).
%
When JavaScript is embedded in web browser engines such as
Gecko or Blink, or in server-side platforms such as Node.js, additional
APIs such as the Document Object Model (DOM) or the file system
get exposed as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

@@

We leverage contexts to implement |specLangJS seqf| for Node.js.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library and our IFC primitives (|send|, |sandbox|, etc.).
%
In turn, these tasks can create new tasks with |sandbox|.
%
Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
the global object corresponding to the standard JavaScript library and
our IFC primitives.

>>>>

JavaScript, as specified by
ECMAScript~\cite{ecma}, does not have any built-in
functionality for I/O
(we denote this language as |targetLangJS|).
%
When JavaScript is embedded in web browser engines such as
Gecko or Blink, or in server-side platforms such as Node.js, additional
APIs such as the Document Object Model (DOM) or the file system
get exposed as part of the runtime system.
%
In a similar manner, we can directly implement the embedded language
|specLangJS roundrobinf| by exposing (only) our IFC primitives as part
of the runtime and running multiple instances of the JavaScript VM in
separate OS-level threads.\footnote{
  We, indeed, do this for the Gecko implementation when considering
  Web Workers that run operate OS threads.
}
%
Unfortunately, this becomes very costly when an application relies on
many tasks.
%
(Consider, for instance, a server-side web application that wishes to
create a new task for each HTTP request.)

@@

\subsubsection{Server-side embedding for Node.js}

Using contexts as the unit of isolation, we implemented
|specLangJS seqf| for Node.js.
%
Our implementation provides a library for creating new tasks, i.e.,
contexts whose global object only contains the standard JavaScript
library and our IFC primitives (|send|, |sandbox|, etc.).
%
In turn, these tasks can create new tasks with |sandbox|.
%
Formally, |sandbox| is defined with |klone(tS) = tS0|, where |tS0| is
the global object corresponding to the standard JavaScript library and
our IFC primitives.
